Multi-Domain Adaptation in Neural Machine Translation with Dynamic Sampling Strategies

### 2021-05-14 2021/emnlp/auto_cl_mdmt.tex
change comments in section results

\subsection{Domain Adaptation}\label{ssec:da}
In this setting, we aim to build an expert NMT model in only one domain. This setting corresponds to Dirac distribution $\lambda^t$, in which the probability of domains is 0 except for one domain.

We initialize MDAC and DDS by 3 different distributions $\lambda_0$, $\lambda_1$ and $\lambda_d$. According to Table \ref{tab:da}, MDAC achieves the best performance with $\lambda_0$ initial where all domains have the same probability to be chosen, though $\lambda_0$  initialization only improve significantly $\lambda_d$ initialization in small domains including \domain{talk},\domain{bank}and\domain{it}. $\lambda_d$ initialization is beneficial for adapting the NMT system to large domains such as \domain{med} and \domain{law}. The same conclusion is also true for DDS.

>>>>

\subsection{Domain Adaptation}\label{ssec:da}
In this setting, we aim to build an expert NMT model in only one domain. This corresponds to setting $\vlambda^t$ to a deterministic distribution, in which the probability of all domains is $0$ except for one domain. We denote this distribution $\vlambda_d$, with $d$ the domain of interest.

We initialize MDAC and DDS in 3 ways, using $\vlambda_0$, $\vlambda_1$ and $\vlambda_d$. According to Table~\ref{tab:da}, MDAC achieves the overall best performance when $\vlambda_{t=0} = \vlambda_0$.  Doing so proves significantly better than initializing with $\lambda_d$ for the small domains: \domain{talk}, \domain{bank} and\domain{it}. Conversely, initializing with $\lambda_d$ is beneficial when targeting large domains such as \domain{med} and \domain{law}. The same conclusion also holds for DDS.
